Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2020-01-30 analysis/paper/paper.Rmd
Kevin added something to the discussion.
I undid the random comment I made.
deleted one section in discussion.

## What Models Are Currently Available?

@@

## Model Assumptions

Model assumptions should always be considered when interpreting results; the following assumptions were made when modeling habitat capacity using QRF methods. First, we assumed that sites with higher carrying capacity (i.e., ‘better’ habitat) contain more parr during fish surveys. Second, we assumed that carrying capacity is a function of habitat. Third, we assumed that estimates of parr densities from fish surveys are unbiased. Fourth, we assumed that at least some sites in our dataset were at or close to local carrying capacity at the site level. However, if this fourth assumption is not met, we will obtain a conservative estimate of carrying capacity (but the framework of the model is not wrong). Finally, we assumed that the 90th quantile of predictions at each CHaMP site is a reasonable proxy for carrying capacity. With insufficient data, it is difficult to get a well-defined estimate of higher quantiles because substantial amounts of data are necessary to define the tails of a distribution.

<!-- This paragraph needs to be hashed out.	 -->
Assumptions we don’t need to make. Because QRF naturally incorporates non-linear relationships between predictor and response variables, we make no assumptions regarding the shape of fish-habitat relationships. Rather, fish-habitat relationships are estimated from the data with no *a priori* constraints. Moreover, we make no assumptions regarding correlations among habitat covariates; the random forest framework accounts for possible interactions between habitat metrics, so we don’t need to explicitly place them in the model.

>>>>

## What Watershed-scale Capacity Models Are Currently Available?

@@

<!-- Try to include images of high capacity / low capacity sites  -->
